Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome

### 2023-06-05 paper/paper.qmd
Do need to explicitly set inline hook
Inline hook only works part of the time on render??
Move tables & figures to near in-text refs

schtools::set_knitr_opts()

@@

We thank the patients for donating stool samples and the research
team members that who collected, stored, and processed the samples.

@@

# Tables

#  Figures

>>>>

knitr::knit_hooks$set(inline = schtools::inline_hook)

@@

We thank the patients for donating stool samples and the research team members
who collected, stored, and processed the samples.

@@
